\cvsection{Employment}

\begin{cventries}

  \cventry
  {Laboratory of Planetology and Geodynamics (LPG)}
  {CNRS Research engineer}
  {Nantes, France}
  {Nov. 2020 - Present}
  {
    \begin{cvitems}
      \item{Development of \cvwebsite{https://moon-coverage.readthedocs.io}{coverage analysis} tool for ESA‑JUICE mission, under contract with ESA.}
    \end{cvitems}
    \vspace{1em}
  }

  \cventry
    {Jet Propulsion Laboratory (NASA/JPL-Caltech)}
    {Post-doctoral researcher}
    {Pasadena, CA USA}
    {Oct. 2018 - Oct. 2020}
    {
      \begin{cvitems}
        \item{Mapping of Titan's specular relexions during the Cassini mission.}
        \item{Analysis of lossy compression on hyperspectral datasets for outer-planets exploration.}
        \item{Characterization of Titan's clouds and haze structure}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Laboratory of Planetology and Geodynamics (LPG)}
    {Research engineer / Post-doctoral researcher}
    {Nantes, France}
    {Jan. - Sept. 2018}
    {
      \begin{cvitems}
        \item{Development of the
        \cvwebsite{https://vims.univ-nantes.fr/}{Cassini VIMS Data Portal},
        a web interface for the calibrated Cassini-VIMS dataset.}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Group of Molecular and Atmospheric Spectroscopy (GMSA)}
    {Research engineer}
    {Reims, France}
    {Oct. - Dec. 2017}
    {
      \begin{cvitems}
        \item{Development of analysis tools for the Cassini-ISS instrument.}
      \end{cvitems}
      \vspace{1em}
    }

\end{cventries}
