\cvsection{Research Internships}

\begin{cventries}

  \cventry
    {Cassini high resolution navigation with star catalogues}
    {Supervisor: Robert A. West}
    {JPL, Pasadena, USA}
    {Mar. -- Apr. 2017}
    {
      \begin{cvitems}
        \item{Full calibration and deconvolution of ISS data}
        \item{Star navigation with the Tycho \& GAIA catalogues}
      \end{cvitems}
    }

  \cventry
    {Modeling radar response of Linear Dunes and Mega-Yardangs on Earth and Titan}
    {Supervisor: Philippe Paillou}
    {LAB, Bordeaux, France}
    {Jan. -- Jul. 2014}
    {
      \begin{cvitems}
        \item{Cassini and TerraSAR-X radar image analysis}
        \item{SRTM and GDEM data processing}
        \item{Radar backscattering modeling}
      \end{cvitems}
    }

  \cventry
    {Cassini VIMS image processing on Titan}
    {Supervisor: Christophe Sotin}
    {NASA/JPL, Pasadena, USA}
    {May -- Aug. 2013}
    {
      \begin{cvitems}
        \item{Hyperspectral infrared image processing}
        \item{Image navigation and mapping}
        \item{Gravitational fields analysis}
      \end{cvitems}
    }

  \cventry
    {Analysis on stable tungsten isotopes in iron meteorites}
    {Supervisors: Breton Thomas \& Quitté Ghylaine}
    {ÉNSL, Lyon, France}
    {Jan. -- Apr. 2013}
    {
      \begin{cvitems}
        \item{Iron meteorites sampling}
        \item{Isotopic chemistry extraction}
        \item{ICP mass spectrometry}
      \end{cvitems}
    }

  \cventry
    {Characterization of thermal history on primitive meteorites}
    {Supervisor: Lydie Bonal}
    {IPAG, Grenoble, France}
    {Jun. -- Jul. 2012}
    {
      \begin{cvitems}
        \item{Carbon micro-meteorites sampling}
        \item{IR and RAMAN spectroscopy}
        \item{MEB and synchrotron imaging (ESRF)}
      \end{cvitems}
    }

  \cventry
    {Morphology studies on Martian barchans based on MRO/CTX images}
    {Supervisor: Pascal Allemand}
    {LGLTPE, Lyon, France}
    {Jun. -- Jul. 2012}
    {
      \begin{cvitems}
        \item{MRO CTX data processing}
        \item{Image mapping and stereoscopy reconstruction}
      \end{cvitems}
    }

  \cventry
    {Telescopic Interferometry applied to planetary and stellar measurements}
    {Supervisors: Éric Thiébault \& Jacque Valade}
    {CRAL, Lyon, France}
    {Apr. 2009 -- Jun. 2011}
    {
      \begin{cvitems}
        \item{Telescopic survey of Jupiters' moons}
        \item{Interferometry modeling}
      \end{cvitems}
    }

\end{cventries}
